---
title: "Seurat Data Integration from .rds Files"
author: "Tapan Baral"
date: "Current Date"
output:
  html_document:
    toc: true
    toc_float: true
---

# Introduction

This R Markdown document demonstrates how to integrate multiple single-cell RNA-seq datasets stored as .rds files using Seurat.

## Load Required Libraries

```{r load_libraries, echo=FALSE, message=FALSE}
library(Seurat)
library(patchwork)
```

## List .rds files in the directory
```{r,  echo=FALSE}
args <- commandArgs(trailingOnly=TRUE)
input_dir   <- args[1]
output_dir  <- args[2]
rds_files <- list.files(input_dir, pattern = "\\.rds$", full.names = TRUE)
```


## Load .rds files into a list

```{r, echo=FALSE}
rds_objects <- lapply(rds_files, readRDS)
```


## Perform data preprocessing (e.g., normalization, scaling) for each dataset

 rds_objects <- lapply(rds_objects, function(x) {
    x <- NormalizeData(x)
    x <- FindVariableFeatures(x, selection.method = "vst", nfeatures = 2000)
   return(x)
 })

## Find integration anchors
```{r, echo=FALSE}
anchors <- FindIntegrationAnchors(object.list = rds_objects)
```

##  Integrate datasets

```{r, echo=FALSE}
integrated_data <- IntegrateData(anchorset = anchors)
```

```{r, echo=FALSE}
dir.create(basename(dirname(output_dir)), showWarnings = FALSE)

saveRDS(integrated_data, file = "integratedData.rds")
```



